\section{OSGi Dependencies}

CIShell is built to be run in a fully compliant OSGi Service Platform R4
implementation. In addition to the base OSGi implementation, several
optional OSGi services are required to be available in a fully compliant CIShell
implementation. Each additional required service is described in the OSGi
Service Platform Service Compendium
R4\footnote{http://www.osgi.org/Release4/Download}.

\subsection*{Required Services}
\begin{description}
  \item[Metatype Service] as described in OSGi section 105 ``Metatype Service
  Specification,'' this service defines the \class{MetaTypeProvider} class used
  for specifying user interfaces in CIShell. In addition, it provides an XML 
  format for automatically generating \class{MetaTypeProvider}s and a service,
 \class{MetaTypeService}, for harvesting them for use by bundles.
  \item[Log Service] as described in OSGi section 101 ``Log Service 
  Specification,'' this service is used as a universal logging system for 
  algorithms and services. See chapter \ref{logService} for more details.   
  \item[Preferences Service] as described in OSGi section 106 ``Preferences
  Service Specification,'' this service is used as a universal preference
  storage system for algorithms and services. See chapter \ref{preferencesService} for
  more details.
  \item[Configuration Admin Service] \comments{More details when the expanded
  prefs spec is done\ldots}
\end{description}

\subsection*{Recommended Services}
\begin{description}
  
  \item[Declarative Services] as described in OSGi section 112 ``Declarative
  Services Specification,'' this service can be used by CIShell algorithms to
  simplify algorithm service registration and for finding necessary auxilary services.\item[]
\end{description}
