%% Cyberinfrastructure Shell (CIShell) Core Specification
%%
%% Copyright 2006,2007,2008 Indiana University
%%
%% Licensed under the Apache License, Version 2.0 (the "License");
%% you may not use this file except in compliance with the License.
%% You may obtain a copy of the License at
%%
%%     http://www.apache.org/licenses/LICENSE-2.0
%%
%% Unless required by applicable law or agreed to in writing, software
%% distributed under the License is distributed on an "AS IS" BASIS,
%% WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
%% See the License for the specific language governing permissions and
%% limitations under the License.
%%
%

\section{OSGi Dependencies}

CIShell is built to be run in a fully compliant OSGi Service Platform R4
implementation. In addition to the base OSGi implementation, several
optional OSGi services are required to be available in a fully compliant CIShell
implementation. Each additional required service is described in the OSGi
Service Platform Service Compendium
R4\footnote{http://www.osgi.org/Release4/Download}.

\subsection*{Required Services}
\begin{description}
  \item[Metatype Service] is described in OSGi section 105 ``Metatype Service
  Specification.'' This service is used by CIShell to find
  \class{MetaTypeProviders} for user interface specification, user-adjustable
  preferences, and input parameters. It also provides an XML format for
  automatically generating \class{MetaTypeProvider}s which the 
  \class{MetaTypeService} harvests for use.
  \item[Log Service] is described in OSGi section 101 ``Log Service 
  Specification.'' This service is used as a universal logging system for 
  algorithms and services. See chapter \ref{logService} for more details.   
  \item[Preferences Service] is described in OSGi section 106 ``Preferences
  Service Specification.'' This service is used as a universal preference
  storage system for algorithms and services. See chapter \ref{preferencesService} for
  more details.
  \item[Configuration Admin Service] is described in OSGi section 104
  ``Configuration Admin Service Specification.'' This service is used as a
  manager/provider of configuration information for bundles and services. It is 
  useful for meeting the User Adjustable Preferences (section
  \ref{userPrefsSpec}) requirements.
\end{description}

\subsection*{Recommended Services}
\begin{description}
  \item[Declarative Services] is described in OSGi section 112 ``Declarative
  Services Specification.'' This service can be used by CIShell algorithms to
  simplify algorithm service registration and for finding necessary auxilary services.
\end{description}
